Improved Smooth Free-Form Deformation with Sharp Feature Awareness

### 2016-08-22 paper.tex
add error pic to paper
add color map to error
add error table

\subsection{Approximation error tests}
not finish!!!!!!!!!!!!!!!!!!!!

In the smooth FFD, both the geometry and normal are obtained approximately via constrained fitting. Thus, there
are approximation errors in the geometry and normal compared with the accurate FFD. Since the smooth parts of a
polygonal object can be regarded as a piecewise linear approximation of a potentially smooth shape, which is unknown in
general, thus it is difficult to evaluate the approximation errors.

Here, we use a Cube model and a Utah teapot model consists of 36 bicubic B\'ezier patches to test the approximation
error, because the geometry and normal of both the input objects are defined accurately. Both of the two models are
normalized into $[-1,1]^3$. The deformations of the Cube model by \cite{Cui13} and \cite{Cui14} are accurate for both
the geometry and normal. The accurate deformation result of Utah teapot is obtained via original FFD of uniformly
sampled points and normals. The input of smooth FFD of the Utah teapot is a mesh generated via de Casteljau
subdivisions. The error test results are shown in Figure~\ref{fig:error}, where the first and second columns are the
Cube model deformed by a $2\times2\times2$ and $3\times3\times3$ B-spline volume, respectively. The third column is the
Utah teapot deformed by a $2\times2\times2$ B-spline volume. For clarity, the shading differences are inverted and
enhanced by 10 times, as shown in Figure~\ref{fig:error}(d).

The statistics of geometry error, normal error and volume error are given in
Tables~\ref{tab:error_vertex}-\ref{tab:error_volume}, respectively. The geometry error is the Euclidean distances
between the corresponding vertices, and the normal error is the angles between the corresponding normals. The volume
error of Utah teapot is not listed here because it's not a closed model.

According to Figure~\ref{fig:error} and Table~\ref{tab:error_vertex}-\ref{tab:error_volume}, the proposed smooth FFD can
generate good approximations of accurate FFD from the geometry, normal, and volume aspects. Among them, only maximum
normal error of the Utah teapot model is a little bit large. The maximum errors only occur at the spout end and lip
which are high curvature parts. Here the input mesh of the Utah teapot is obtained via uniform sampling approach, thus
it is not a good polygonal approximation to its original smooth model. It leads to the maximum normal approximation
error as above. That is to say the maximum error comes from the polygonal mesh approximation to the smooth object, which
is out of scope of the paper. 
\section{Conclusion and Future Work}

>>>>

\subsection{Approximation error tests}

\begin{figure}
	\centering
    \subfloat[][Original model]{
		\includegraphics[width=0.99\linewidth]{pic/error0.png}}\par
	\subfloat[][Improved Smooth FFD results of (a)]{
		\includegraphics[width=0.99\linewidth]{pic/error2.png}}\par
	\subfloat[][Smooth FFD results of (b)]{
		\includegraphics[width=0.99\linewidth]{pic/error3.png}}\par
\end{figure}

\begin{figure}
    \ContinuedFloat
	\subfloat[][Accurate FFD results of (c)]{
		\includegraphics[width=0.99\linewidth]{pic/error1.png}}\par
	\subfloat[][Improved Smooth FFD's Geometry errors]{
		\includegraphics[width=0.99\linewidth]{pic/error4.png}}\par
	\subfloat[][Improved Smooth FFD's Normal errors]{
		\includegraphics[width=0.99\linewidth]{pic/error5.png}}\par
\end{figure}

\begin{figure}
    \ContinuedFloat
	\subfloat[][Smooth FFD's Geometry errors]{
		\includegraphics[width=0.99\linewidth]{pic/error6.png}}\par
	\subfloat[][Smooth FFD's Normal errors]{
		\includegraphics[width=0.99\linewidth]{pic/error7.png}}
	\caption{Error testing}
	\label{fig:error}
\end{figure}

In the improved smooth FFD as well as smooth FFD, both the geometry and normal are obtained approximately via constrained fitting. Thus, there
are approximation errors in the geometry and normal compared with the accurate FFD. Since the smooth parts of a
polygonal object can be regarded as a piecewise linear approximation of a potentially smooth shape, which is unknown in
general, thus it is difficult to evaluate the approximation errors.

Here, we use a Cube model and a Utah teapot model consists of 36 bicubic B\'ezier patches to test the approximation
error, because the geometry and normal of both the input objects are defined accurately. Both of the two models are
normalized into $[-1,1]^3$. The deformations of the Cube model by \cite{Cui13} and \cite{Cui14} are accurate for both
the geometry and normal. The accurate deformation result of Utah teapot is obtained via original FFD of uniformly
sampled points and normals. The input of smooth FFD of the Utah teapot is a mesh generated via de Casteljau
subdivisions. The error test results are shown in Figure\ref{fig:error}, where the first column are the
Cube model deformed by a $2\times2\times2$ B-spline volume, respectively. The second column is the
Utah teapot deformed by a $2\times2\times2$ B-spline volume.

The statistics of geometry error, normal error and volume error are given in Tables~\ref{tab:error_vertex}-\ref{tab:error_volume}, respectively. The geometry error is the Euclidean distances
between the corresponding vertices, and the normal error is the angles between the corresponding normals.

\begin{table}[htbp]
\begin{center}
	\begin{minipage}[c]{0.47\textwidth}
	\footnotesize
	\centering
	\caption{Cube Geometry approximation errors}
	\begin{tabular}{lll}
		\hline
		& Average error & Maximum error \\
		\hline
			Improved Smooth FFD & 0.002952310 & 0.02908119 \\
			Smooth FFD & 0.004904391 & 0.03718415 \\
		\hline
	\end{tabular}
	\label{tab:error_vertex}
	\end{minipage}
	\begin{minipage}[c]{0.52\textwidth}
	\footnotesize
	\centering
	\caption{Cube Normal approximation errors}
	\begin{tabular}{lll}
		\hline
			& Average error & Maximum error \\
		\hline
			Improved Smooth FFD & 0.5785680$^\circ$ & 15.89719$^\circ$ \\
			Smooth FFD & 0.5853341$^\circ$ & 21.24638$^\circ$ \\
		\hline
	\end{tabular}
	\label{tab:error_normal}
	\end{minipage}
\end{center}
\end{table}

\begin{table}[htbp]
\begin{center}
	\begin{minipage}[c]{0.47\textwidth}
	\footnotesize
	\centering
	\caption{Teapot Geometry approximation errors}
	\begin{tabular}{lll}
		\hline
		& Average error & Maximum error \\
		\hline
			Improved Smooth FFD & 0.006597950 & 0.01203453 \\
			Smooth FFD & 0.006650957 & 0.01220984 \\
		\hline
	\end{tabular}
	\label{tab:error_vertex}
	\end{minipage}
	\begin{minipage}[c]{0.52\textwidth}
	\footnotesize
	\centering
	\caption{Teapot Normal approximation errors}
	\begin{tabular}{lll}
		\hline
			& Average error & Maximum error \\
		\hline
			Improved Smooth FFD & 0.6152188$^\circ$ & 22.53011$^\circ$ \\
			Smooth FFD & 0.5491496$^\circ$ & 22.53010$^\circ$ \\
		\hline
	\end{tabular}
	\label{tab:error_normal}
	\end{minipage}
\end{center}
\end{table}

According to Figure~\ref{fig:error} and Table~\ref{tab:error_vertex}, the proposed improved smooth FFD can
generate good approximations of accurate FFD from the geometry, normal. Among them, only maximum
normal error of the Utah teapot model is a little bit large. The maximum errors only occur at the spout end and lip
which are high curvature parts. Here the input mesh of the Utah teapot is obtained via uniform sampling approach, thus
it is not a good polygonal approximation to its original smooth model. It leads to the maximum normal approximation
error as above. That is to say the maximum error comes from the polygonal mesh approximation to the smooth object, which
is out of scope of the paper.

\section{Conclusion and Future Work}
